A Cost-Aware Approach to Adversarial Robustness in Neural Networks

### 2024-09-11 cover_letter.tex
Updates from Overleaf

\signature{Charles Meyers, \\ Mohammed Reza, \\ Tommy L\"{o}fstedt, \\ and  Erik Elmroth \\ }
\address{Department of \\ Computing Science,\\ Ume\aa University,\\ Sweden}

\begin{document}
\begin{letter}{}
\opening{To whom it may concern}

I am writing you on behalf of the authors of \em{A Cost-Aware Approach to Adversarial Robustness in Neural Networks}, which is the attached manuscript.  In this work, we developed a cloud-native methodology for quickly and precisely modelling the effect of model covariates using accelerated failure time models and a multi-objective search to minimize training cost while maximizing model accuracy. Not only do we provide a detailed outline and related source code, but we show the surprising result that smaller, more power-efficient GPUs create models that are more robust and more cost effective than models built on hardware that is advertised as being more capable. 
\closing{Sincerely,}
\end{letter}
\end{document}

>>>>

\signature{Charles Meyers}
\address{Department of \\ Computing Science,\\ Ume\aa{}~University,\\ Sweden}

\begin{document}
\begin{letter}{}
\opening{Dear Editors,}

I am writing you on behalf of the authors of \textit{A Cost-Aware Approach to Adversarial Robustness in Neural Networks}, which is the attached manuscript.  In this work, we developed a cloud-native methodology for quickly and precisely modelling the effect of model covariates using accelerated failure time models and a multi-objective search to minimize training cost while maximizing model accuracy. Not only do we provide a detailed outline and related source code, but we show the surprising result that smaller, more power-efficient GPUs create models that are more robust and more cost effective than models built on hardware that is advertised as being more capable.

% You can add something about why we submit to this journal (showing that we are in scope and that we think highly of the journal) and that we look forward to a swift processing of the manuscript.)

\closing{On behalf of the authors, sincerely,}
\end{letter}
\end{document}

### 2024-09-11 main.tex
Updates from Overleaf

\author[1]{\fnm{Mohammad} \sur{Reza Saleh Sedghpour}}\email{msaleh@cs.umu.se}

@@

\affil*[1]{\orgdiv{Department of Computing Science}, \orgname{Ume\aa ~University},
\city{Ume\aa}, \postcode{901 87}, \country{Sweden}}

@@

\subsection{Contributions}
To tackle the problems of minimizing deployment cost while maximizing the model performance on both the test set and in the presence of adversarial noise we present a scalable and effective methodology (see  Figure~\ref{fig:experiments}) and software framework (see Figure~\ref{fig:architecture}) for the training (see Section~\ref{aft}) and evaluation (see Section~\ref{cost}) of ML models that:
\begin{itemize}
    \item Optimises for benign and adversarial accuracy simultaneously,
    % \item Extends survival analysis to the realm of neural networks, 
    \item Demonstrates a scalable and effective method to train a model while simultaneously estimating the effect of various hyperparameters, and
    \item Measures the power and monetary cost of deploying a model across different hardware architectures to model the trade-offs between deployment hardware and robustness.
    \item Demonstrates that, even when we separately measure the effect of the slower clock speed of "inference only hardware" compared to hardware tailored for training, that models trained using the "inference only" devices are more robust for image classification tasks than models built on hardware designed for training.
\end{itemize}

@@

@@

% no keywords
% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\clearpage
\section{Availability of Data and Materials}
The source code for conducting the experiments is available in the \texttt{deckard} \href{https://github.com/simplymathematics/deckard/tree/main/examples/power}{ repository} and the pretrained \texttt{pytorch} version of ResNet18 was used to conduct the experiments. Requirements and dependencies are listed within the repository, which is distributed under the GNU Public License version 3. The compiled data and the Python source code for this document are available \href{https://github.com/simplymathematics/kepler-ml}{here}. The source code has been tested on Windows and various Linux distributions and should work on MacOS, but has not been tested there.
\printglossary
\clearpage
\bibliography{sn-bibliography}

>>>>

\author[2]{\fnm{Mohammad} \sur{Reza Saleh Sedghpour}}\email{mohammad.saleh@elastisys.com}

@@

\affil*[1]{\orgdiv{Department of Computing Science}, \orgname{Ume\aa{} University},
\city{Ume\aa{}}, \postcode{901 87}, \country{Sweden}}

@@

\subsection{Contributions}
To tackle the problems of minimizing deployment cost while maximizing the model performance on both the test set and in the presence of adversarial noise we present a scalable and effective methodology (see  Figure~\ref{fig:experiments}) and software framework (see Figure~\ref{fig:architecture}) for the training (see Section~\ref{aft}) and evaluation (see Section~\ref{cost}) of ML models that:
\begin{itemize}
    \item Optimises for benign and adversarial accuracy simultaneously.
    % \item Extends survival analysis to the realm of neural networks, 
    \item Demonstrates a scalable and effective method to train a model while simultaneously estimating the effect of various hyperparameters.
    \item Measures the power and monetary cost of deploying a model across different hardware architectures to model the trade-offs between deployment hardware and robustness.
    \item Demonstrates that, even when we separately measure the effect of the slower clock speed of "inference only hardware" compared to hardware tailored for training, that models trained using the "inference only" devices are more robust for image classification tasks than models built on hardware designed for training.
\end{itemize}

@@

\subsection{Availability of Data and Materials}
The source code for conducting the experiments is available in the \texttt{deckard} \href{https://github.com/simplymathematics/deckard/tree/main/examples/power}{ repository} and the pretrained \texttt{pytorch} version of ResNet18 was used to conduct the experiments. Requirements and dependencies are listed within the repository, which is distributed under the GNU Public License version 3. The compiled data and the Python source code for this document are available \href{https://github.com/simplymathematics/kepler-ml}{here}. The source code has been tested on Windows and various Linux distributions and should work on MacOS, but has not been tested there.

@@

% \clearpage

\printglossary
% \clearpage
\bibliography{sn-bibliography}
